Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2014-12-19 MS_revised.tex
tolweb as reference
fixes comment 4

Species richness data for Nymphalidae genera were compiled from several
sources including the specialist-curated lists on
\url{http://tolweb.org}, Lamas (2004) \cite{lamas2004} and curated lists of
Global Butterfly Names project (\url{http://www.ucl.ac.uk/taxome/gbn/}).
We assigned the species numbers of genera not included in the phylogeny
to the closest related genus that was included in Wahlberg et al. (2009)
\cite{wahlberg2009} study according to available phylogenetic studies 
\cite{matos2013, brower2010, kodandaramaiah2010, kodandaramaiah2010a,
ortiz2013, desilva2010, freitas2004, pena2006, penz1999, silva2008,
pena2011, pena2010},
taxonomical classification and morphological resemblance when no
phylogenies were available (supp. mat. 3).

>>>>

Species richness data for Nymphalidae genera were compiled from several
sources including the specialist-curated lists 
\cite{tolweb2007, lamas2004} and curated lists of the
Global Butterfly Names project \cite{gbnp}.
We assigned the species numbers of genera not included in the phylogeny
to the closest related genus that was included in Wahlberg et al. (2009)
\cite{wahlberg2009} study according to available phylogenetic studies 
\cite{matos2013, brower2010, kodandaramaiah2010, kodandaramaiah2010a,
ortiz2013, desilva2010, freitas2004, pena2006, penz1999, silva2008,
pena2011, pena2010},
taxonomical classification and morphological resemblance when no
phylogenies were available (supp. mat. 3).
